Sufficient Conditions for Reachability in Automata Networks with Priorities

### 2014-04-14 main.tex
fixes in GLC + TODO: remove procs
add 'References' title
minor rewriting of abstract and intro (additions compared to [12])

% Commandes À FAIRE
\usepackage{color} % Couleurs du texte
%\definecolor{darkgreen}{rgb}{0,0.5,0}
%\newcommand{\towrite}[1]{\textcolor{darkgreen}{[#1]}}
%\newcommand{\todo}[1]{\textcolor{red}{\textbf{[#1]}}}

@@

To address this issue, we propose an extended definition of the framework, including priority classes for actions.
In this paper, we focus on a restriction of the Process Hitting with two classes of priorities and a specific behaviour of the components, that is sufficient to tackle the aforementioned problem of cooperations.
We show that this class of Process Hitting models allows to represent any
Asynchronous Discrete Networks, either Boolean or multivalued; and also any
Process Hitting model with arbitrary number of priority classes.
Then we develop a new refinement for the under-approximation of the static analysis to give accurate results for this class of Process Hitting models.
Our method thus allows to efficiently under-approximate reachability properties
in Asynchronous Discrete Networks,
as it is illustrated on the model-checking of a signalling network of 94
components, which is unprecedented.
\end{abstract}
\begin{keyword}
discrete networks \sep
abstract interpretation \sep
reachability \sep
qualitative models \sep
systems biology
\end{keyword}
\end{frontmatter}

@@

\bibliographystyle{elsarticle-num}
\bibliography{biblio}

>>>>

% Commandes À FAIRE
\usepackage{color} % Couleurs du texte
%\definecolor{darkgreen}{rgb}{0,0.5,0}
%\newcommand{\towrite}[1]{\textcolor{darkgreen}{[#1]}}
\newcommand{\todo}[1]{\textcolor{red}{\textbf{[#1]}}}

@@

To address this issue, we propose an extended definition of the framework, including priority classes for actions.
In this paper, we focus on a restriction of the Process Hitting with two classes of priorities and a specific behaviour of the components, that is sufficient to tackle the aforementioned problem of cooperations.
We develop a new refinement for the under-approximation of the static analysis to give accurate results for this class of Process Hitting models.
Then we show that this class of models is sufficient to represent any
Process Hitting model with an arbitrary number of classes of priorities,
and even any Asynchronous Discrete Networks, either Boolean or multivalued.
Our method thus allows to efficiently under-approximate reachability properties
in Asynchronous Discrete Networks,
as it is illustrated on the model-checking of a signalling network of 94
components, which is unprecedented.
\end{abstract}
\begin{keyword}
discrete networks \sep
abstract interpretation \sep
reachability \sep
qualitative models \sep
systems biology
\end{keyword}
\end{frontmatter}

@@

\section*{References}
\bibliographystyle{elsarticle-num}
\bibliography{biblio}

### 2014-04-14 parts/intro.tex
minor rewriting of abstract and intro (additions compared to [12])

The main additions in this paper compared to \cite{FPMR13-CS2Bio} are
two theorems, the first
stating that any Process Hitting model with any number of classes of priorities can be represented
with only two classes of priorities,
and the other giving a method to cope with successive reachability,
both extending the application range of the static analysis we developed.

>>>>

The main additions in this paper compared to \cite{FPMR13-CS2Bio} are
two theorems, the first
stating that any Process Hitting model with any number of classes of priorities can be represented
with only two classes of priorities,
and the other giving a method to cope with successive reachability.
Both aim at extending the application range of the static analysis we developed.
